Inpainting with controlled dimensionality reduction in the Fourier domain

### 2011-06-20 project/Paper/paper.tex
Updated .bib file. Removed unused references

\begin{abstract}
  This paper suggests a novel approach to restore noisy images.
  ((( TODO )))
  The abstract should really be written last, along with the title of
the paper. The four points that should be covered~\cite{jones08}:
\begin{enumerate}
\item State the problem.
\item Say why it is an interesting problem.
\item Say what your solution achieves. (CLAIM!)
\item Say what follows from your solution.
\end{enumerate}
\end{abstract}

@@

  The style in this section should read as if you were verbally
describing the conduct of the experiment. 
The methods section is not a step-by-step, directive,
protocol as you might see in your lab manual, but detailed enough such
that an interested reader can reproduce your
work~\cite{anderson04,wavelab}.
The methods
section should describe what was
done to answer the research question, describe how it was done,
justify the experimental design, and
explain how the results were analyzed.

The methods section of a research paper provides the information by
which a study's validity is judged.
Therefore, it requires a clear and precise description of how an
experiment was done, and the rationale
for why specific experimental procedures were chosen.
It is usually helpful to
structure the methods section by~\cite{kallet04methods}:
\begin{enumerate}
\item Describing the algorithms used in the study, briefly including
  details such as hyperparameter values (e.g. thresholds), and
  preprocessing steps (e.g. normalizing the data to have mean value of
  zero).
\item Explaining how the materials were prepared, for example the
  images used and their resolution.
\item Describing the research protocol, for example which examples
  were used for estimating the parameters (training) and which were
  used for computing performance.
\item Explaining how measurements were made and what
  calculations were performed. Do not reproduce the full source code in
  the paper, but explain the key steps.
\end{enumerate}

@@

 We compare our algorithm with the following two baseline algorithms:
 \begin{enumerate}
 \item A simple inpainting algorithm using (((TODO )))
 \item A matching pursuit algorithm with a dictionary consisting of (((TODO)))
 \end{enumerate}

@@

\paragraph{Note}
All plots in this paper were created with MATLAB$\textsuperscript{\textregistered}$ and can be reproduced using the script 'CreatePaperPosts.m' in our submission.\\

>>>>

\begin{abstract}
  This paper suggests a novel approach to restore noisy images.
  ((( TODO )))
  The abstract should really be written last, along with the title of
the paper. The four points that should be covered:
\begin{enumerate}
\item State the problem.
\item Say why it is an interesting problem.
\item Say what your solution achieves. (CLAIM!)
\item Say what follows from your solution.
\end{enumerate}
\end{abstract}

@@

  The style in this section should read as if you were verbally
describing the conduct of the experiment. 
The methods section is not a step-by-step, directive,
protocol as you might see in your lab manual, but detailed enough such
that an interested reader can reproduce your
work.
The methods
section should describe what was
done to answer the research question, describe how it was done,
justify the experimental design, and
explain how the results were analyzed.

The methods section of a research paper provides the information by
which a study's validity is judged.
Therefore, it requires a clear and precise description of how an
experiment was done, and the rationale
for why specific experimental procedures were chosen.
It is usually helpful to
structure the methods section by:
\begin{enumerate}
\item Describing the algorithms used in the study, briefly including
  details such as hyperparameter values (e.g. thresholds), and
  preprocessing steps (e.g. normalizing the data to have mean value of
  zero).
\item Explaining how the materials were prepared, for example the
  images used and their resolution.
\item Describing the research protocol, for example which examples
  were used for estimating the parameters (training) and which were
  used for computing performance.
\item Explaining how measurements were made and what
  calculations were performed. Do not reproduce the full source code in
  the paper, but explain the key steps.
\end{enumerate}

@@

 We compare our algorithm with the following two baseline algorithms:
 \begin{enumerate}
	 \item A simple linear inpainting algorithm using the nearest neighbor pixels.
	 \item A matching pursuit algorithm \cite{matchingpursuit93} with an overcomplete dictionary consisting of Discrete Cosine transforms.
 \end{enumerate}

@@

\paragraph{Note}
All plots in this paper were created with MATLAB$\textsuperscript{\textregistered}$ and can be reproduced using the script 'CreatePaperPlots.m' in our submission.\\
